\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

\usepackage[hidelinks]{hyperref}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{amsmath,amssymb,amsbsy,amsfonts}
\usepackage{accents}
\usepackage{nicefrac}
\usepackage{upgreek}
\usepackage[]{footmisc}

\input{macros}

\setcounter{MaxMatrixCols}{20}

\begin{document}

% \title{Improving State Estimation of a Landing Vehicle From a Multirotor UAV
% Using Feature Tracking}
\title{\LARGE \bf
Improving State Estimation of a Landing Vehicle \\
From a Multirotor UAV Using Feature Tracking
}

\author{Michael~Farrell
        and~Tim~McLain
\thanks{The research was supported by the National Science Foundation STTR Phase II: Autonomous Landing of Small Unmanned Aircraft Systems onto Moving Platforms, Award No. IIP-1758678 in partnership with Planck Aerosystems.}
\thanks{Michael Farrell is an M.S. student in the Department of Mechanical
Engineering, Brigham Young University, Provo, UT, 84602, USA.}% <-this % stops a space
\thanks{Tim McLain is a Professor in the Department of Mechanical
Engineering, Brigham Young University, Provo, UT, 84602, USA.}% <-this % stops a space
}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

\begin{abstract}
  We propose an error-state Kalman filter to improve the state estimation of a
  landing vehicle as observed by an approaching multirotor unmanned aerial
  vehicle (UAV). As is common, we
  assume that the landing vehicle is outfitted with a fiducial landing marker.
  In addition to measurements from the fiducial landing marker, the proposed
  estimator uses measurements of visual features which are tracked in the UAV's
  camera frame. We assume that these tracked visual features are rigidly
  attached to the landing vehicle such that they provide information to the
  filter about the relative pose from the UAV to the landing vehicle. We show
  in both simulation and hardware experiments that the addition of these visual
  features to the filter allows for accurate and consistent estimates of the
  state of the landing vehicle even when the fiducial landing marker is not
  detected for significant periods of time.
\end{abstract}

\section{Introduction} \label{sec:intro}
% Big Picture
% Why important, what, why hard?
% Thecnical gaps
% Drones operating from static world
% Why drones operating/landing on moving vehicles
\input{introduction/background}
% Different approaches with fiducial markers - IBVS, Big Competition
% Visual Inertial Odometry - ROVIO, VINS-MONO, etc
% \input{introduction/related_work}
\input{introduction/paper_layout}

\section{Mathematical Conventions} \label{sec:model}
\input{model/notation}
\input{model/quaternions}
\input{model/s1}
% \input{model/quadrotor_dynamics}
% \input{model/landing_vehicle_dynamics}

\section{Estimation} \label{sec:estimation}
\input{estimation/estimator}
\input{estimation/dynamics}
\input{estimation/initialization}
\input{estimation/measurements}
% \input{estimation/normal_depth_estimator}

% \section{Control} \label{sec:control}

\section{Simulation} \label{sec:simulation}
\input{simulation/simulation}

\section{Hardware} \label{sec:hardware}
\input{hardware/platform}
% \input{hardware/control}
\input{hardware/aruco}
\input{hardware/feature_tracking}
\input{hardware/mocap}
\input{hardware/landing_vehicle}
\input{hardware/results}

\section{Conclusion} \label{sec:conclusion}
The proposed estimator provides a method for maintaining accurate and consistent
estimates of the state of a landing vehicle when a fiducial landing marker is
not detected for significant periods of time. This improvement is achieved by
tracking and estimating the locations of unknown visual features on the landing
vehicle. The simulation and hardware experiments show that by tracking and
estimating the locations of just 10 visual features, the multirotor UAV can
continue to reliably operate with respect to the landing vehicle for long
periods of time without detecting the fiducial landing marker.

% \appendices
% \section{Proof of the First Zonklar Equation}
% Appendix one text goes here.

% \section{}
% Appendix two text goes here.

% \section*{Acknowledgment}
% The authors would like to thank...

\bibliographystyle{IEEEtran}
\bibliography{abbrev,library}

\end{document}


