% !TEX root=./root.tex

% The propsed estimator estimates both the state of
% the UAV and the state of the landing vehicle as well as the positions of visual
% landmarks on the landing vehicle.
% in the same Error-State Kalman
% filter~\cite{sola2017quaternion}.
We express the state of the estimated system as the tuple
\begin{equation*}
  \hat{\x} =
  \begin{pmatrix}
    \hat{\x}_{\text{UAV}}, \hat{\x}_{\text{Goal}}, \hat{\x}_{\text{Features}}
  \end{pmatrix}
\end{equation*}
with the components defined as
\begin{align*}
  \hat{\vect{x}}_{\text{UAV}} &=
  \begin{pmatrix}
    \hat{\vect{p}}_{b/I}^{I}, \hat{\vect{q}}_I^{b}, \hat{\vect{v}}_{b/I}^b,
    \hat{\vect{\beta}}_a,
    \hat{\vect{\beta}}_{\omega}
  \end{pmatrix} \\
    & \qquad \qquad \in \mathbb{R}^3 \times S^3 \times \mathbb{R}^3 \times \mathbb{R}^3 \times
    \mathbb{R}^3  \\
  % \x_{\text{UAV}} &=
  % \begin{bmatrix}
    % \vect{p}_{b/I}^I &
    % \phi & \theta & \psi &
    % \vect{v}_{b/I}^b &
    % \mu & \vect{\beta}_a & \vect{\beta}_\omega
  % \end{bmatrix}^\transpose \\
    \hat{\x}_{\text{Goal}} & =
    \begin{pmatrix}
      \hat{\vect{p}}_{g/b}^{v}, \hat{\vect{v}}_{g/I}^{g}, \hat{\psi}_{I}^{g},
      \hat{\omega}_{g/I}^{g}
    \end{pmatrix}
    \in \mathbb{R}^3 \times \mathbb{R}^2 \times S^1 \times \mathbb{R}^1
    \\
    \hat{\x}_{\text{Features}} & =
    \begin{pmatrix}
      \hat{\vect{r}}_{1/g}^{g}, \dots \hat{\vect{r}}_{n/g}^{g}
    \end{pmatrix}
    \in \mathbb{R}^3 \dots \mathbb{R}^3.
\end{align*}
The inputs to the estimated system are given by
\begin{equation*}
  \vect{u} = \begin{pmatrix} \bar{\vect{a}}_{b/I}^I, \bar{\vect{\omega}}_{b/I}^b \end{pmatrix} \in
        \mathbb{R}^3 \times \mathbb{R}^3,
\end{equation*}
which are directly measured from an inertial measurement unit mounted on the UAV.

The estimated states associated with the UAV, $\hat{\vect{x}}_{\text{UAV}}$,
contain the traditionally estimated states of position, attitude, and velocity
in addition to bias states for the accelerometer and gyroscope sensors.

The estimated states associated with the landing vehicle,
$\hat{\vect{x}}_{\text{Goal}}$, contain the position, attitude, velocity, and
angular velocity of the landing vehicle.
We note that the
estimated position of the landing vehicle is relative to the position of the
UAV. This relative state is observable even with poor estimates of the UAV's global
position, $\hat{\vect{p}}_{g/I}^I$, because of the relative information provided
by the measurements as described in~\secref{sec:measurement_models}.
% Note that $\hat{\vect{x}}_{\text{UAV}}$ contains the same states mentioned previously
% in~\secref{sec:UAV_dynamics} with the addition of $\hat{\vect{\beta}}_a$ and
% $\hat{\vect{\beta}}_\omega$, the estimated bias vectors for the acclerometer and
% gyroscope sensors. On the
% other hand, $\hat{\vect{x}}_{\text{Goal}}$ varies 
% from the landing vehicle states mentioned in~\secref{sec:landing_veh_dynamics}
% by containing $\hat{\vect{p}}_{g/b}^v$ instead of $\hat{\vect{p}}_{b/I}^I$.
% % as well as $\hat{\vect{r}}_{1/g}^{g} \dots \hat{\vect{r}}_{n/g}^{g}$.
% We estimate the relative state, $\hat{\vect{p}}_{g/b}^v$, instead
% of the global state, $\hat{\vect{p}}_{g/I}^I$, as the relative state is observable
% even with poor estimates of the UAV's global position, $\hat{\vect{p}}_{b/I}^I$.

The estimated vectors $\hat{\vect{r}}_{1/g}^{g} \dots \hat{\vect{r}}_{n/g}^{g}$ represent the
locations of visual features $1 \dots n$ which are rigidly attached to the
landing vehicle. We show in our simulation and hardware experiments, that the
addition of these visual features to the estimated state allows the estimator
to maintain accurate and consistent estimates of $\hat{\x}_{\text{Goal}}$ even
while the fiducial landing marker is not detected for long periods of time. 

We note
that the estimated state is of dynamic size. As visual features are
detected they are added to the state vector until a maximum size of the state
vector is reached. As the visual features leave the field of view of the camera
or are otherwise no longer tracked, they are removed from the estimated state
vector to make room for new visual features to be added.

% In the following
% subsections, we define the error-state of the estimated system,  thdescribe the dynamic equations used to model the state of the
% estimated system, the
% initialization of certain states, and the specific
% measurement models used to update the filter.

% As mentioned in~\secref{sec:intro??} the estimation of these
% visual landmarks allows the estimator to maintain accurate and consistent
% estimates of the landing vehicle even while the fiducial landing marker is not
% detected for long periods of time.

\subsection{Error-State Definition}

As the estimated state is not a vector, but rather a tuple of Lie groups, we
employ the error-state Kalman filter (ESKF) as described in~\cite{koch2017relative}.
% The error-state of the estimated system is defined by
We define the error-state of the estimated system as
\begin{align*}
  \tilde{\vect{x}} =&
  \left[ \begin{matrix}
    \tilde{\vect{p}}_{b/I}^{I}, \tilde{\vect{\theta}}_I^{b}, \tilde{\vect{v}}_{b/I}^b,
    \tilde{\vect{\beta}}_a,
    \tilde{\vect{\beta}}_{\omega},
    \tilde{\vect{p}}_{g/b}^{v}, \tilde{\vect{v}}_{g/I}^{g}, \tilde{\psi}_{I}^{g},
    \tilde{\omega}_{g/I}^{g},
    \end{matrix}\right. \\
    & \qquad \left. \begin{matrix}
      \tilde{\vect{r}}_{1/g}^{g}, \dots \tilde{\vect{r}}_{n/g}^{g}
  \end{matrix} \right]
  \in \mathbb{R}^{22 + 3n}
\end{align*}
with the error-state components related to the vector states, $\x_{\vect{v}}$, defined with
the vector subtraction operator as
\begin{equation}
\tilde{\x}_{\vect{v}} \triangleq \x_{\vect{v}} - \hat{\x}_{\vect{v}}
\label{eq:vector_error_state}
\end{equation}
such that
\begin{equation}
  \tilde{\vect{p}}_{b/I}^I = \vect{p}_{b/I}^I - \hat{\vect{p}}_{b/I}^I.
\end{equation}
We reiterate that we treat $\psi_I^g \in S^1$ as a vector space such that
\begin{equation}
  \tilde{\psi}_I^g = \psi_I^g - \hat{\psi}_I^g.
\end{equation}
We follow~\cite{koch2017relative}, defining the error-state of the quaternion
$\hat{\q}_I^b$ as the minimal representation
\begin{equation}
  \tilde{\vect{\theta}}_I^b \triangleq \log_{\q} \left( \left( \hat{\q}_I^b \right)^{-1}
  \otimes \q_I^b \right),
  \label{eq:quat_error_state}
\end{equation}
which also results in
\begin{equation}
  \q_I^b  = \hat{\q}_I^b \otimes \exp_{\q} \left( \tilde{\vect{\theta}}_I^b
  \right).
  \label{eq:quat_true_state}
\end{equation}


