% !TEX root=./root.tex

\subsection{Goal and Landmark Initialization}
The goal states are initialized upon receiving the first measurement from
the detection of the fiducial landing marker. We assume that we can measure the
relative translation and rotation from the camera to the fiducial marker
at each detection. This measurement,
\begin{equation}
  \bar{\vect{z}} =
  \begin{bmatrix}
    \bar{\vect{p}}_{g/c}^c & \bar{\vect{q}}_c^g,
  \end{bmatrix}
  \label{eq:fiducial_meas}
\end{equation}
is used to initialize the goal states with
\begin{align}
  \hat{\vect{p}}_{g/b}^v &= \left( \hat{R}_I^b \right)^\transpose \left( \left ( R_b^c
  \right)^\transpose \bar{\vect{p}}_{g/c}^c + \vect{p}_{c/b}^b
\right)   \\
      \hat{\theta_I^g} &= yaw \left( \bar{R}_c^g R_b^c \hat{R}_I^b \right)
  % quat::Quatd q_I2g_meas = x().q * q_b2c_ * z.q_c2a * q_a2g;
  % const double yaw_meas = q_I2g_meas.euler()(2);
\end{align}
where $R_b^c$ and $\vect{p}_{c/b}^b$ are assumed to be known constants and
$yaw()$ is a function that extracts the yaw Euler angle from a rotation matrix.
The linear and angular velocity of the landing vehicle are initialized to values
of zero with large enough covariances for the specific use case.

Similar to the manner in which the goal states are intialized, each time a new
landmark is added to the estimated vector, we initialize its state based on the
first measurement received. As we only receive measurements of the pixel
location of the visual landmark,
\begin{equation}
  \vect{z} = \begin{bmatrix} \bar{p}_x & \bar{p}_y \end{bmatrix}
  \label{eq:pixel_meas}
\end{equation}
depth is not measured. Therefore, to initialize
the landmark states, we assume that the landmark lies in the $xy$ plane of the
goal frame. The $z$ component of $\vect{r}_{i/g}^g$ is initialized to zero and a
large enough covariance is selected for the specific use case. To compute the
$x$ and $y$ components of $\vect{r}_{i/g}^g$, we start with the pinhole camera
model. We assume that the pixel measurements in~\eqref{eq:pixel_meas} have been
rectified to compensate for lens distortion such that
\begin{equation}
  \begin{bmatrix}
    p_x \\ p_y \\ 1
  \end{bmatrix} = \frac{1}{\e_3^\transpose \vect{p}_{i/c}^c} K \vect{p}_{i/c}^c \\
\end{equation}
where $K$ is the camera intrisic matrix. If we invert $K$ and multiply by both
sides, we get
\begin{equation}
 \frac{1}{\e_3^\transpose \vect{p}_{i/c}^c} \vect{p}_{i/c}^c
  =
  K^{-1} \begin{bmatrix}
    p_x \\ p_y \\ 1
  \end{bmatrix}
\end{equation}
which is equivalent to
\begin{equation}
 \vect{p}_{i/c}^v
  =
  \left( \e_3^\transpose \vect{p}_{i/c}^c \right) \left( R_I^b
  \right)^\transpose \left( R_b^c \right)^\transpose K^{-1} \begin{bmatrix}
    p_x \\ p_y \\ 1
  \end{bmatrix}.
\end{equation}
As $\e_3^\transpose \vect{p}_{i/c}^c$ is unknown, we define 
\begin{equation}
  \scaled{\vect{p}}_{i/c}^v
  =
   \left( R_I^b
  \right)^\transpose \left( R_b^c \right)^\transpose K^{-1} \begin{bmatrix}
    p_x \\ p_y \\ 1
  \end{bmatrix},
\end{equation}
which is equivalent to $\vect{p}_{i/c}^v$ up to a scale factor. As previously
mentioned, we estimate this scale factor by assuming that $\e_3^\transpose
\vect{r}_{i/g}^g = 0$. This means that
\begin{align}
  \e_3^\transpose \hat{\vect{p}}_{i/c}^v &= \e_3^\transpose \hat{\vect{p}}_{g/b}^v -
  \e_3^\transpose \left( \hat{R}_I^b \right)^\transpose \hat{\vect{p}}_{c/b}^b
  \\
  \hat{\vect{p}}_{i/c}^v &= \frac{\e_3^\transpose
  \hat{\vect{p}}_{i/c}^v}{\e_3^\transpose \scaled{\vect{p}}_{i/c}^v} \scaled{\vect{p}}_{i/c}^v
  \\
    \hat{\vect{p}}_{i/b}^v &= \hat{\vect{p}}_{i/c}^v + \left( R_I^b \right)^\transpose \vect{p}_{c/b}^b \\
    \hat{\vect{r}}_{i/g}^g &= \hat{R}_I^g \left( \hat{\vect{p}}_{i/b}^v -
    \hat{\vect{p}}_{g/b}^v \right).
\end{align}

% \begin{align}
  % \begin{bmatrix}
    % p_x \\ p_y \\ 1
  % \end{bmatrix} &= \frac{1}{\e_3^\transpose \vect{p}_{i/c}^c} K \vect{p}_{i/c}^c \\
  % \begin{bmatrix}
    % X^c / Z^c \\
    % Y^c / Z^c \\
    % 1
  % \end{bmatrix}
   % &= K^{-1}
  % \begin{bmatrix}
    % p_x \\ p_y \\ 1
  % \end{bmatrix} \\
  % \begin{bmatrix}
    % X^c / Z^c \\
    % Y^c / Z^c \\
    % 1
  % \end{bmatrix}^v
   % &= R_b^v R_c^b K^{-1}
  % \begin{bmatrix}
    % p_x \\ p_y \\ 1
  % \end{bmatrix} \\
% \end{align}
% The resulting vector, $
  % \begin{bmatrix}
    % X^c / Z^c \\
    % Y^c / Z^c \\
    % 1
  % \end{bmatrix}^v$
  % is the vector $\vect{p}_{i/c}^v$ up to a scale factor. The vector can be scaled by assuming that the altitude of the landmark is equal to the
% altitude of the goal. To get the expected altitude, we solve for
% \begin{align}
  % \e_3^\transpose \vect{p}_{g/c}^v &= \e_3^\transpose \vect{p}_{g/b}^v - \e_3^\transpose \vect{p}_{c/b}^v \\
  % \e_3^\transpose \vect{p}_{g/c}^v &= \e_3^\transpose \vect{p}_{g/b}^v -
  % \e_3^\transpose R_b^I \vect{p}_{c/b}^b \\
  % \e_3^\transpose \vect{p}_{g/c}^v &= \frac{1}{\rho_g} -
  % \e_3^\transpose R_b^I \vect{p}_{c/b}^b \\
% \end{align}

% This gives us the vector, $\vect{p}_{i/c}^v$.
% With this vector, we can then reach the estimated state vector,
% $\vect{p}_{i/g}^g$ with the following
% \begin{align}
  % \vect{p}_{i/v}^v &= \vect{p}_{i/c}^v + R_b^I \vect{p}_{c/b}^b \\
  % \vect{p}_{i/g}^g &= R_v^g \left( \vect{p}_{i/v}^v - \vect{p}_{g/v}^v \right).
% \end{align}

